### 2015-05-14 background.tex
improvements in bg

Example~\ref{fig:data_race_example} presents multiple data races that \whoop automatically found in the generic\_nvram Linux char driver (see \S\ref{evaluation}). The driver can invoke the \texttt{nvram\_llseek} entry point concurrently from two threads $T_1$ and $T_2$, while passing the same \texttt{file} object as a parameter. However, this can lead to multiple possible data races, because $T_1$ and $T_2$ can access the \texttt{f\_pos} field of the \texttt{file} object in arbitrary order.

@@

The most common technique for eliminating data races is using a \emph{locking} mechanism. Locking a set of program statements that access a shared resource creates a \emph{critical section}, i.e.\ source code that cannot be executed by more than one thread simultaneously. Figure~\ref{fig:lock_example} shows how to use a lock to eliminate the data race in Figure~\ref{fig:data_race_example}. The example is tricky, because the return statement can potentially race on the \texttt{f\_pos} field. To fix this issue, we store the result in a temporary variable, inside the critical section.

>>>>

Example~\ref{fig:data_race_example} shows a racy entry point that \whoop (see \S\ref{whoop}) automatically found in the generic\_nvram Linux char driver (see \S\ref{evaluation}). The driver can invoke the \texttt{nvram\_llseek} entry point concurrently from two threads $T_1$ and $T_2$, while passing the same \texttt{file} object as a parameter. However, this can lead to multiple possible data races, because $T_1$ and $T_2$ can access the \texttt{f\_pos} field of the \texttt{file} object in arbitrary order.

@@

The most common technique for eliminating races is using a \emph{locking} mechanism. Locking a set of program statements that access a shared resource with a lock $l$ creates a \emph{critical section}, i.e.\ source code that cannot execute concurrently by threads that hold $l$. Figure~\ref{fig:lock_example} shows how to use a lock to eliminate the data race in Figure~\ref{fig:data_race_example}. The example is tricky, because the return statement can potentially race on the \texttt{f\_pos} field. To fix this issue, we store the result in a temporary variable, inside the critical section.
